---
title: "Programming Assignment #1"
output: html_document
---

## Task 1: Create input and output vectors

For this part of the assignment you should create a vector `x` that contains the values `1 2 3 4 5`, as well as a vector `y` that contains the values `11 18 31 39 47` in the R code chunk below.

```{r}
x <- c(1,2,3,4,5)
y <- c(11,18,31,39,47)
```


## Task 2: Create a dataframe

For this part of the assignment create a dataframe `df` of x and y. You can plot the dataframe to help visualize in the R code chunk below:

```{r}
df <- data.frame(x,y)
print(df)
plot(df)
```

## Task 3: Determine slope and y-intercept 

For this part of the assignment you should generate a line of best fit using `lm()` and store the slope in a variable  `slope` and the y-intercept in a variable `y_int` rounded to a single decimal in the R code chunk below. If you would like you can plot the dataframe and line of best fit to help visualize.

```{r}
plot(df)
abline(lm(y~x))
y_int <- coef(lm(y~x))[[1]]
y_int <- round(y_int, 1)
print(y_int)
slope <- coef(lm(y~x))[[2]]
slope <- round(slope, 1)
print(slope)
```

## Grading Rubric:
Please note for this assignment you are being autograded on the following 5 objects:

* `x` vector
* `y` vector
* `df` dataframe
* `y_int` scalar value
* `slope` scalar value